---
title: "Intro to Mfactors"
author: "Melissa Guzman"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Intro to Mfactors}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Mfactors is a package designed to make factors less painful. It consists of four main functions:  

* fbind  
* freq_out  
* fac_as_is  
* fread_csv  

## Installation
```{r, message = FALSE}
#install.packages("devtools")
devtools::install_github("lmguzman/MelissaFactors")
library(Mfactors)
```

## Usage

### fbind

`fbind()` makes sure that the levels of the two factors are also binded together. 
```{r}
fbind(iris$Species[c(1, 51, 101)], PlantGrowth$group[c(1, 11, 21)])
```

### freq_out

`freq_out()` Is the equivalent from dplyr for count. It tally's up the different categories on a factor. 
```{r}
freq_out(iris$Species)
```

### fac_as_is

`fac_as_is()` creates a factor, but it leaves the levels as they appear on the data and not in alphabetical order.

```{r}
x <- c('candy', 'wont', 'make', 'me', 'sick')
levels(factor(x))
levels(fac_as_is(x))
```

### fread_csv

`fread_csv()` reads a csv but checks all columns that are imported as factors. If the number of levels in the factor is equal to the length of the column, then it becomes a character type. Othewise is left as a factor. All of the arguments passed onto `read.csv()` are available on `fread_csv()` plus an extra argument to check the factor. 

```{r}
tenletters <- factor(letters[1:10])
tf <- tempfile()
write.csv(tenletters, tf)

character_reading <- fread_csv(tf, check.factor = TRUE)
str(character_reading)

factor_reading <- fread_csv(tf, check.factor = FALSE)
str(factor_reading)
```



